



\bibitem[L: StegoGeschichte]{L: StegoGeschichte} 
\url{https://igw.tuwien.ac.at/designlehren/steganographie.pdf} \\
Eine kurze Geschichte der Steganographie \\ 
Peter Purgathofer \\
12.11.2016

\bibitem[L: Stego VS Crypto]{L: Stego VS Crypto}
\url{http://digilib.happy-security.de/files/Steganographie.pdf} \\
Kryptographie und Informationstheorie: Steganographie \\
Prof. Dr. Richard Eier, Institut für Computertechnik TU Wien\\
Michaela Schuster\\
20.11.2016 

\bibitem[L: StegoVersteck]{L: StegoVersteck}
\url{http://www.tecchannel.de/a/vertrauliche-daten-perfekt-versteckt,2024281} \\
Vertrauliche Daten perfekt versteckt, Artikel vom 30.11.2009 \\
13.12.2016

\bibitem[L: USA-Crypto Export]{L: USA-Crypto Export}
\url{https://en.wikipedia.org/wiki/Export_of_cryptography_from_the_United_States}

\bibitem[L-Confidentiality without Encryption]{L-Confidentiality without Encryption}
\url{http://people.csail.mit.edu/rivest/chaffing-980701.txt} \\
Chaffing and Winnowing: Confidentiality without Encryption \\
Ronald L. Rivest \\
MIT Lab for Computer Science \\
March 18, 1998 (rev. July 1, 1998) \\

\bibitem[L-Convolution]{L-Convolution}
\url{http://colah.github.io/posts/2014-07-Understanding-Convolutions}
Understanding Convolutions \\
Christopher Olah \\
30.03.2017

\bibitem[L-Convolution-Kernels]{L-Convolution-Kernels}
\url{http://matlabtricks.com/post-5/3x3-convolution-kernels-with-online-demo}\\
30.03.2017

\bibitem[L-Stego]{L-Stego}
Jessica Fridrich: Steganography in Digital Media: Principles, Algorithms, and Applications \\
Cambridge University Press (12 Nov 2009) \\
ISBN: 978-052119019-0 \\
30.03.2017

\bibitem[L-Jpeg-Algorithm]{L-Jpeg-Algorithm}
 \url{http://www-i6.informatik.rwth-aachen.de/web/Misc/Coding/365/li/material/notes/Chap4/Chap4.2/Chap4.2.html}
%http://www2.units.it/ipl/students_area/imm2/files/JPEG/p30-wallace.pdf
30.03.2017

\bibitem[L-JSteg]{L-JSteg}
\url{http://cise.ufl.edu/~makumar/proposalppt.pdf} \\
Steganography and Steganalysis of JPEG Images\\
Ph.D. Proposal \\
Mahendra Kumar \\
CISE Department
30.03.2017

\bibitem[L-Fehlererkennung]{L-Fehlererkennung}
\url{http://web.mit.edu/course/16/16.682/www/leca.pdf}
30.03.2017

\bibitem[L-Peterson]{L-Peterson}
W. W. Peterson: Cyclic Codes for Error Detection. \\
In: Proceedings of the IRE, Vol. 49, No. 1, 1961, S. 228-235

\bibitem[L-AES-Encryption-Standard]{L-AES-Encryption-Standard}
\url{http://nvlpubs.nist.gov/nistpubs/FIPS/NIST.FIPS.197.pdf}
30.03.2017

\bibitem[L-Kongruenzgenerator]{L-Kongruenzgenerator}
 Donald E. Knuth: The Art of Computer Programming. \\ 
 Volume 2 Seminumerical Algorithms. 3. Auflage. Addison-Wesley \\
 1997, S. 10-26\\ 
 ISBN 0-201-89684-2 

